### 2008-08-04 doc/backend_interface/Backends.tex
backends doc update

The information system interface consists of set of Perl scripts which
generates an XML output to \texttt{STDOUT}.

@@

The information collector scripts are divided between several separate scripts:
\begin{itemize}
\item \texttt{cluster+qju.pl} - driver for information collection. It calls all other information collectors and prints results in XML. The information collection is done by one single invocation of this script
\item \texttt{InfoCollector.pm} - base class for all information collectors (i.e.: all files \texttt{*Info.pm}).
\item \texttt{InfoChecker.pm} - used by InfoCollector to validate options and results against a sort of ``schema'', as implemented by \texttt{InfoChecker.pm}.
\item \texttt{GMJobsInfo.pm} - collects information about jobs from grid manager status files
\item \texttt{HostInfo.pm} - collects other information that can be collected on the front end (hostname, software version, disk space for users, installed certificates, Runtime environments ...)
\item \texttt{LRMSInfo.pm} - collects information that is LRMS specific (queues, jobs, local user limits ...) by calling the appropriate LRMS plugin. It also does validation of input options to the plugin and of the data returned by the plugin. 
\item \texttt{BATCH\_SYSTEM\_NAME.pm} - plugins for LRMSInfo. Only Fork, SGE and PBS are updated to the new framework
\item \texttt{ARC0ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the classic NG schema
\item \texttt{ARC1ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the GLUE2 schema
\item \texttt{ARC0ClusterSchema.pm} - ``schema'' of the info produced by ARC0ClusterInfo
\item \texttt{ARC1ClusterSchema.pm} - ``schema'' of the info produced by ARC1ClusterInfo
\end{itemize}

@@

This function is called without arguments and should return a ``schema'' hash
declaring the configuration options specific for this LRMS plugin. This
``schema'' conforms to the format understood by \texttt{InfoChecker.pm} and is
used to validate input options by \texttt{LRMSInfo.pm}.

@@

\texttt{lrms\_info} returns all LRMS specific information. This
includes information about the cluster, queues, jobs and local users. The
function is called with an options hash of hashes. It should then return an
hash of hashes with the following keys and the appropriate value.

\begin{table}
\caption{The \texttt{lrms\_info} hash} \label{t:lrms_info}
\begin{center}
\begin{tabular}{|c|c|}
\hline
key & value\\
\hline \hline
lrms\_type & the type of LRMS e.g PBS\\
\hline
lrms\_version & the version of the LRMS\\
\hline
totalcpus & total number of CPUs in the cluster\\
\hline
queuedcpus & total number of CPUs requested by LRMS queuing jobs (both grid and
non-grid)\\
\hline
usedcpus & CPUs in the LRMS that are currently in use either by grid or
non-grid jobs\\
\hline
cpudistribution & number of CPUs in a node and number of each type e.g.
{}``8cpu:5 2cpu:100''\\
\hline
queues & a hash with keys being queue names and values being
\texttt{queue\_info} hashes as described in table \ref{t:queue_info} \\
\hline
jobs & a hash with keys being LRMS job IDs and values being
\texttt{jobs\_info} hashes as described in table \ref{t:jobs_info} \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{The \texttt{queue\_info} hash}
\label{t:queue_info}
\begin{center}
\begin{tabular}{|c|c|}
\hline
key & value\\
\hline \hline
status & available slots in queue, negative number signals error\\
\hline
maxrunning & limit on number of running jobs\\
\hline
maxqueuable & limit on number of jobs queued on this queue\\
\hline
maxuserrun & limit on number of running jobs per user\\
\hline
maxcputime & limit on maximum CPU time for a job in this queue in minutes\\
\hline
mincputime & limit on minimum CPU time for a job in this queue in minutes\\
\hline
efaultcput & default CPU time limit for a job in this queue in minutes\\
\hline
maxwalltime & limit on maximum wall time for a job in this queue in minutes\\
\hline
minwalltime & limit on minimum wall time for a job in this queue in minutes\\
\hline
defaultwallt & default wall time limit for a job in this queue in minutes\\
\hline
running & number of CPUs used by running jobs (both grid and non-grid) in the
queue\\
\hline
queued & number of CPUs requested by queuing jobs in the queue\\
\hline
totalcpus & number of CPUs available to the queue\\
\hline
users & a hash with keys being local UNIX user names and values being
\texttt{users\_info} hashes as described in table \ref{t:users_info} \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{The \texttt{users\_info} hash}
\label{t:users_info}
\begin{center}
\begin{tabular}{|c|c|}
\hline
key & value\\
\hline \hline
freecpus & number of freely available CPUs with their time limits in minutes
(see ComputingService.FreeSlotsWithDuration in\cite{glue2})\\
\hline
queuelength & estimated queue length for the specified user\\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{The \texttt{jobs\_info} hash}
\label{t:jobs_info}
\begin{center}
\begin{tabular}{|c|c|}
\hline
key & value\\
\hline \hline
status & LRMS jobstatus mapping\footnotemark[1]:
Running->'R', Queued->'Q', Suspended->'S', Exiting->'E', Other->'O'\\
\hline
rank & the job's position in the LRMS queue\\
\hline
mem & the memory usage of the job in kBs\\
\hline
walltime & consumed wall-time in minutes\\
\hline
cputime & consumed CPU-time in minutes\\
\hline
reqwalltime & wall-time requested by job in minutes\\
\hline
reqcputime & CPU-time requested by job in minutes\\
\hline
nodes & list of execution hosts\\
\hline
comment & array of string comments about the job in LRMS, can be an empty
array\\
\hline
\end{tabular}
\footnotetext[1]{LRMS job states mapping is described in\cite{is}}
\end{center}
\end{table}

@@

\begin{itemize}
\item The node definition can be checked by \texttt{<PBS installation path>/bin/pbsnodes
-a.} All the nodes MUST have ntype=cluster. 
\item The required queue attributes can be checked as \texttt{<PBS installation
path>/bin/qstat -f -Q queuename.} There MUST be a max\_user\_run or
a max\_running attribute listed with a REASONABLE value. 
\end{itemize}

@@

\phantomsection
%\addcontentsline{toc}{subsubsection}{LocalID}
\hspace*{0.5cm}
\begin{shaded}
\textbf{LocalID}
\end{shaded}
\begin{tabular}{lp{10cm}}  
Attribute value:& LocalID\_t\\
Example:&  \verb#TODO#\\
Related xRSL:& \verb#NA#\\
UI role:& TODO \\

\end{tabular}

Description: An opaque identifier local to the Computing Service.

\phantomsection
%\addcontentsline{toc}{subsubsection}{Name}
\hspace*{0.5cm}
\begin{shaded}
\textbf{Name}
\end{shaded}
\begin{tabular}{lp{10cm}}  
Attribute value:& String\\
Example:& \verb#Name: TODO#\\
Related xRSL:& TODO\\
UI role:& ?\\
\end{tabular}

Description: Name of the application environment.

\phantomsection
%\addcontentsline{toc}{subsubsection}{Version}
\hspace*{0.5cm}
\begin{shaded}
\textbf{Version}
\end{shaded}
\begin{tabular}{lp{10cm}}  
Attribute value:& String\\
Example:& \verb#Version: TODO#\\
Related xRSL:& TODO\\
UI role:& TODO\\
\end{tabular}

Description: Version of the application environment.

@@

@@

>>>>

The information system interface consists of a set of Perl scripts which
generates an XML output to \texttt{STDOUT}.

@@

The information collector scripts are divided between several separate scripts:
\begin{itemize}
\item \texttt{cluster+qju.pl} - driver for information collection. It calls all other information collectors and prints results in XML. The information collection is done by one single invocation of this script
\item \texttt{InfoCollector.pm} - base class for all information collectors (i.e.: all files \texttt{*Info.pm}).
\item \texttt{InfoChecker.pm} - used by \texttt{InfoCollector} to validate options and results against a ``schema''.
\item \texttt{GMJobsInfo.pm} - collects information about jobs from grid manager status files
\item \texttt{HostInfo.pm} - collects other information that can be collected on the front end (hostname, software version, disk space for users, installed certificates, Runtime environments ...)
\item \texttt{LRMSInfo.pm} - collects information that is LRMS specific (queues, jobs, local user limits ...) by calling the appropriate LRMS plugin. It also does validation of input options to the plugin and of the data returned by the plugin. 
\item \texttt{BATCH\_SYSTEM\_NAME.pm} - plugins for LRMSInfo. Only Fork, SGE and PBS are updated to the new framework
\item \texttt{ARC0ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the classic NG schema
\item \texttt{ARC1ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the GLUE2 schema
\end{itemize}

@@

This function is called without arguments and should return a ``schema'' hash
declaring the configuration options specific for this LRMS plugin. This
``schema'' conforms to the format understood by \texttt{InfoChecker.pm} and is
used to validate input options to the plugin.

@@

The \texttt{lrms\_info} function returns all LRMS specific information. This
includes information about the cluster, queues, jobs and local user limits. The
function is called with a hash of hashes containing all options required by the
LRMS plugin. Some options are common to all plugins, and are described in table
\ref{t:lrms_opts}.

\begin{table}
\caption{The \texttt{lrms\_options} hash used as input for the \texttt{lrms\_info} function} \label{t:lrms_opts}
\begin{center}
\begin{tabular}{|c|p{12cm}|}
\hline
key & value\\
\hline \hline
jobs & array with local job IDs \\
\hline
queues & hash with queue names as keys and values being
\texttt{queue\_options} hashes (table \ref{t:queue_opts}) \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{The \texttt{queue\_options} hash} \label{t:queue_opts}
\begin{center}
\begin{tabular}{|c|p{12cm}|}
\hline
key & value\\
\hline \hline
users & array with local UNIX user names \\
\hline
\end{tabular}
\end{center}
\end{table}

The \texttt{lrms\_info} function should then return a
hash of hashes with the sctructure described in table \ref{t:lrms_info}.

\begin{table}
\caption{The \texttt{lrms\_info} hash returned by the \texttt{lrms\_info} function} \label{t:lrms_info}
\begin{center}
\begin{tabular}{|c|p{12cm}|}
\hline
key & value\\
\hline \hline
lrms\_type & the type of LRMS e.g PBS\\
\hline
lrms\_version & the version of the LRMS\\
\hline
totalcpus & total number of CPUs in the cluster\\
\hline
queuedcpus & total number of CPUs requested by LRMS queuing jobs (both grid and
non-grid)\\
\hline
usedcpus & CPUs in the LRMS that are currently in use either by grid or
non-grid jobs\\
\hline
cpudistribution & number of CPUs in a node and number of each type e.g.
{}``8cpu:5 2cpu:100''\\
\hline
queues & a hash with keys being queue names and values being
\texttt{queue\_info} hashes as described in table \ref{t:queue_info} \\
\hline
jobs & a hash with keys being LRMS job IDs and values being
\texttt{jobs\_info} hashes as described in table \ref{t:jobs_info} \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{The \texttt{queue\_info} hash}
\label{t:queue_info}
\begin{center}
\begin{tabular}{|c|p{12cm}|}
\hline
key & value\\
\hline \hline
status & available slots in queue, negative number signals error\\
\hline
maxrunning & limit on number of running jobs\\
\hline
maxqueuable & limit on number of jobs queued on this queue\\
\hline
maxuserrun & limit on number of running jobs per user\\
\hline
maxcputime & limit on maximum CPU time for a job in this queue in minutes\\
\hline
mincputime & limit on minimum CPU time for a job in this queue in minutes\\
\hline
efaultcput & default CPU time limit for a job in this queue in minutes\\
\hline
maxwalltime & limit on maximum wall time for a job in this queue in minutes\\
\hline
minwalltime & limit on minimum wall time for a job in this queue in minutes\\
\hline
defaultwallt & default wall time limit for a job in this queue in minutes\\
\hline
running & number of CPUs used by running jobs (both grid and non-grid) in the
queue\\
\hline
queued & number of CPUs requested by queuing jobs in the queue\\
\hline
totalcpus & number of CPUs available to the queue\\
\hline
users & a hash with keys being local UNIX user names and values being
\texttt{users\_info} hashes as described in table \ref{t:users_info} \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{The \texttt{users\_info} hash}
\label{t:users_info}
\begin{center}
\begin{tabular}{|c|p{12cm}|}
\hline
key & value\\
\hline \hline
freecpus & number of freely available CPUs with their time limits in minutes
(see ComputingService.FreeSlotsWithDuration in\cite{glue2})\\
\hline
queuelength & estimated queue length for the specified user\\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{The \texttt{jobs\_info} hash}
\label{t:jobs_info}
\begin{center}
\begin{tabular}{|c|p{12cm}|}
\hline
key & value\\
\hline \hline
status & LRMS jobstatus mapping\footnotemark[1]:
Running $\Rightarrow$ 'R',
Queued $\Rightarrow$ 'Q',
Suspended $\Rightarrow$ 'S',
Exiting $\Rightarrow$ 'E',
Other $\Rightarrow$ 'O'\\
\hline
rank & the job's position in the LRMS queue\\
\hline
mem & the memory usage of the job in kBs\\
\hline
walltime & consumed wall-time in minutes\\
\hline
cputime & consumed CPU-time in minutes\\
\hline
reqwalltime & wall-time requested by job in minutes\\
\hline
reqcputime & CPU-time requested by job in minutes\\
\hline
nodes & list of execution hosts\\
\hline
comment & array of string comments about the job in LRMS, can be an empty
array\\
\hline
\end{tabular}
\footnotetext[1]{LRMS job states mapping is described in\cite{is}}
\end{center}
\end{table}

@@

\begin{itemize}
\item The node definition can be checked by \texttt{<PBS installation path>/bin/pbsnodes
-a.} All the nodes MUST have ntype=cluster. 
\item The required queue attributes can be checked as \texttt{<PBS installation
path>/bin/qstat -f -Q queuename}. There MUST be a max\_user\_run or
a max\_running attribute listed with a REASONABLE value. 
\end{itemize}

@@

Hardcoded Properties:

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Value \\
\hline \hline
Capability & \texttt{executionmanagement.jobexecution} \\
\hline
Type & \texttt{org.nordugrid.arex} \\
\hline
QualityLevel & \texttt{development} \\
\hline
Complexity & \texttt{endpoint=1,share=N,resource=1}, where N is the number of queues in the configuration file\\
\hline
\end{tabular}

\vspace*{3mm}
The following properties referring to job counts are obtained from GridManager's status files:

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Meaning \\
\hline \hline
TotalJobs & Number of grid jobs which are not yet finished \\
\hline
RunningJobs & Number of grid jobs running \\
\hline
WaitingJobs & Number of grid jobs queued in the LRMS and waiting to be submitted to the LRMS \\
\hline
\end{tabular}

@@

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Value\\
\hline \hline
URL & \texttt{https://\emph{hostname}:\emph{port}/arex} \\
\hline
Technology & \texttt{webservice} \\
\hline
Interface & \texttt{OGSA-BES} \\
\hline
WSDL & \texttt{https://\emph{hostname}:\emph{port}/arex/?wsdl} \\
\hline
Semantics & \texttt{http://www.nordugrid.org/documents/arex.pdf} \\
\hline
SupportedProfile & \texttt{WS-I 1.0} and \texttt{HPC-BP} \\
\hline
Implementor & \texttt{NorduGrid} \\
\hline
ImplementationName & \texttt{ARC1} \\
\hline
ImplementationVersion & \texttt{0.9} \\
\hline
QualityLevel & \texttt{development} \\
\hline
HealthState & \texttt{ok} -- no detection of problems yet\\
\hline
ServingState & \texttt{draining} if the configuration has allownew=no, \texttt{production} otherwise \\
\hline
IssuerCA & from the \emph{hostcert.pem} file \\
\hline
TrustedCA & from scanning the \emph{certificates} directory \\
\hline
Staging & \texttt{staginginout} \\
\hline
JobDescription & \texttt{ogf:jsdl:1.0}\\
\hline
\end{tabular}

@@

A ComputingShare element is generated for each 'queue' section in the configuration.

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Value\\
\hline \hline
BaseType & \texttt{Share} \\
\hline
Name & from the configuration \\
\hline
Description & ``comment'' configuration option \\
\hline
MappingQueue & from the configuration \\
\hline
\end{tabular}

\vspace*{3mm}
The following properties are taken from the corresponding values returned by
the LRMS plugin. Units are converted as necessary.

\begin{tabular}{|l|p{12cm}|}
\hline
Property & LRMS plugin property \\
\hline \hline
MaxCPUTime & maxcputime \\
\hline
MinCPUTime & mincputime \\
\hline
DefaultCPUTime & defaultcput \\
\hline
MaxWallTime & maxwalltime \\
\hline
MinWallTime & minwalltime \\
\hline
DefaultWallTime & defaultwallt \\
\hline
\end{tabular}

\vspace*{3mm}

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Value\\
\hline \hline
MaxTotalJobs & maxjobs from configuration\\
MaxRunningJobs & \\
MaxWaitingJobs & \\
\hline
\end{tabular}

\phantomsection
%\addcontentsline{toc}{subsubsection}{Name}
\hspace*{0.5cm}
\begin{shaded}
\textbf{Name}
\end{shaded}
\begin{tabular}{lp{10cm}}  
Attribute value:& String\\
Example:& \verb#Name: TODO#\\
Related xRSL:& TODO\\
UI role:& ?\\
Description:& Name of the application environment\\
\end{tabular}

\phantomsection
%\addcontentsline{toc}{subsubsection}{Version}
\hspace*{0.5cm}
\begin{shaded}
\textbf{Version}
\end{shaded}
\begin{tabular}{lp{10cm}}  
Attribute value:& String\\
Example:& \verb#Version: TODO#\\
Related xRSL:& TODO\\
UI role:& TODO\\
Description:& Name of the application environment\\
\end{tabular}
